Practical Machine Learning Project

The goal of the project is to predict the manner in which they did the exercise from the given data set. This is the "classe" variable in the training set. 

In this project, I will first find the columns which does not contain many NAs and then caclulate the correlation coefficients of the remaining variables. Then I will abstract the important variables from random forest machine learning algorithm and train models.

```{r}
training <- read.csv("pml-training.csv")
testing <- read.csv("pml-testing.csv")

head(training)
names(training)
library(caret)
set.seed(333);

nrow(training)
nrow(testing)
```
create cross validation data set and delete unrelated columns

```{r}
inTrain <- createDataPartition(y=training$classe, p=0.75,list=FALSE)
tr <- training[inTrain,-1:-7]
cv <- training[-inTrain,-1:-7]
```
find the NAs in each column
```{r}
NA_num <- colSums(is.na(tr))
tr_colInd <- ((NA_num/dim(tr)[1]) < 0.05)
tr <- tr[,tr_colInd]
dim(tr)
```
Now the variables has been constrained to 86 variables
```{r}
corInd <- findCorrelation(cor(tr[sapply(tr, is.numeric)]), cutoff=0.4)
tr <- tr[, -corInd]
dim(tr)
```
after deleting all the highly correlated ones, there are 64 variable left
By using a smaller set of the obersavations, I will find the important varialbes
```{r}
var <- train(classe ~ ., data = tr, method = "rf",tuneLength=15)
var_imp <- varImp(var)


modelFit <- train(classe~., 
                  data=tr,
                  method="rf",
                  preProcess=c("center","scale"))
```
Now we can calculate the in-sample error using the confusionMatrix
```{r}
confusionMatrix(training$classe, predict(modelFit, newdata=training))
```

Conclusion, the random forest machine learning method works well in prediciton and gives us a machine learning model for their activities

